Making Sequential Programs Deterministic

### 2019-03-26 design.tex
extending det checker

\subsection{Annotating more classes/providing more specifications}\label{annotating-jdk}
\begin{itemize}
    \item Type system developer has to annotate methods in the JDK or any other library.
    \item Note: Another source of Nondeterminism we haven't analyzed: File system.
    \item Users can also provide stubs instead. (Steal some text from manual here)
\end{itemize}

>>>>

\subsection{Extending the determinism checker}\label{extending-det-checker}
We have primarily focused on collections and annotated the corresponding classes in the JDK.
These annotations provide machine verifiable specifications of determinism properties.
Another source of nondeterminism that we haven't analyzed closely is the File system methods.
A program analysis developer interested in verifying determinism guarantees with respect to 
the File system can easily do so by annotating the parameter and return types of those methods in the JDK.
Alternatively, a user can write these annotations in a \textit{stub} file and supply it to the type checker. A \textit{stub}
only needs to contain method declarations along with their annotations.
